### 2024-08-28 paper.tex
get a good start on section 7

Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
From the first equation we find that
\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
\[\sum_i h_{ii} = 0.\]
Remark: this is just the statement that \(h \in \spl_n\); in other words, we will see that every choice of \(\spl_2\)-triple in \(\gl_{m + n}\) is also an \(\spl_2\)-triple in \(\spl_{m + n}\).
This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
So we have determined \(h\); it is 
\[h = \begin{pmatrix}
    n - 1  & \\
    & n - 3 \\
    & & \ddots \\
    & & & 3 - n \\
    & & & & 1 - n 
\end{pmatrix}.\]
Now, we can use our expression for \(f\) in terms of \(h\) to obtain
\[f = \begin{pmatrix}
    0 & 1 - n \\
    & 0 & (1 - n) + (3 - n) \\
    & & \ddots & \ddots \\
    & & & 0 & (1 - n) + \cdots + (n - 1) \\
    & & & & 0
\end{pmatrix} = \]
\[\begin{pmatrix}
    0 & 1 (1 - n) \\
      & 0 & 2 (2 - n) \\
    & & 0 & (n - 2) (-2) \\
    & & & 0 & (n - 1) (-1)\\
    & &  & & 0
\end{pmatrix}.\]
\end{proof}

@@

Let \(\mathcal{Q}' = \{(A_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).

@@

\subsection{Conclusion}
\begin{theorem}
    The irreducible components of \(\mathcal{Q}\) are the closures of the subvarieties \(\mathcal{Q}_{I, (\rho_i), \alpha}\), as we let \(I, (\rho_i)\) range over all possibilities satisfying the conditions (1)--(4) of \cref{bs_union}, and we let \(\alpha \in \mathrm{SYT}(\mu(I, (\rho_i)))\).
\end{theorem}
\begin{proof}
    We see from \cref{u_i_rho_irred_and_dim} that the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
    Then \cref{bs_union} tells us that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
\end{proof}

\section{The components of \(\mathcal{P}_{J(\lambda)}\)}
Apply things from the previous two sections, and conclude.

>>>>

Note that \([h', e'] = 2e'\), and \([e', f'] = h'\), and \([h', f'] = -2f'\).
Thus \(e, h, f\) must obey the same relations.
In particular, \(he - eh = 2e\).  
The matrix \(eh\) is \(h\) shifted down one, and \(he\) is \(h\) shifted left one.
Thus, \(2e_{ij} = (he - eh)_{ij} = h_{i, j + 1} - h_{i - 1, j}\).
We can use this to show that \(h_{ij} = 0\) when \(i \neq j\).
Then we can use it to show that \(h_{ii} = h_{i - 1, i - 1} + 2\), so that \(h_{ii} = h_{11} + 2(i - 1)\).
\par Similarly, from \([e, f] = h\) we get that \(h_{ij} = (ef - fe)_{ij} = f_{i - 1, j} - f_{i, j + 1}\).
We can use this to show that \(f_{ij} = 0\) when \(j \neq i + 1\).
Then we can use it to show that \(f_{i,i + 1} = f_{i + 1, i + 2} + h_{i + 1, i + 1}\), that \(f_{1,2} = -h_{1, 1}\), and that \(f_{n - 1, n} = h_{n,n}\).
From the first equation we find that
\[-h_{1,1} = f_{1, 2} = f_{n - 1, n} + \sum_{i = 1}^{n - 1} h_{ii} = \sum_{i = 1}^{n} h_{ii} \implies\]
\[\sum_i h_{ii} = 0.\]
(That is, \(h \in \spl_n\).)
This shows that \(h_{11} = n - 1, h_{22} = n - 3, ..., h_{nn} = 1 - n\).
So we have determined \(h\); it is 
\[h = \begin{pmatrix}
    n - 1  & \\
    & n - 3 \\
    & & \ddots \\
    & & & 3 - n \\
    & & & & 1 - n 
\end{pmatrix}.\]
Now, we can use our expression for \(f\) in terms of \(h\) to obtain
\[f = \begin{pmatrix}
    0 & 1 - n \\
    & 0 & (1 - n) + (3 - n) \\
    & & \ddots & \ddots \\
    & & & 0 & (1 - n) + \cdots + (n - 1) \\
    & & & & 0
\end{pmatrix} = \]
\[\begin{pmatrix}
    0 & 1 (1 - n) \\
      & 0 & 2 (2 - n) \\
    & & 0 & (n - 2) (-2) \\
    & & & 0 & (n - 1) (-1)\\
    & &  & & 0
\end{pmatrix}.\]
\end{proof}

@@

(TODO: explain that \(A'\) is like \(A\), but with \(m',n'\) taking the place of \(m,n\).)
Let \(\mathcal{Q}' = \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A_{X', 0, b} V_{i + 1} \subseteq V_i\}\).
\begin{lemma}\label{a_zero}

@@

\subsection{Conclusion}
\begin{theorem}\label{Q_comps}
    The irreducible components of \(\mathcal{Q}\) are the closures of the subvarieties \(\mathcal{Q}_{I, (\rho_i), \alpha}\), as we let \(I, (\rho_i)\) range over all possibilities satisfying the conditions (1)--(4) of \cref{bs_union}, and we let \(\alpha \in \mathrm{SYT}(\mu(I, (\rho_i)))\).
\end{theorem}
\begin{proof}
    We see from \cref{u_i_rho_irred_and_dim} that the \(\mathcal{Q}_{I, (\rho_i), \alpha}\) are irreducible and equidimensional.
    Then \cref{bs_union} tells us that their union is \(\mathcal{Q}\), and in addition that none is contained in the union of the others.
\end{proof}

\section{The components of \(\mathcal{P}_{J(\lambda)}\)}
As in section 5, we write \(X = J(\lambda) \in \gl_m\), where \(\lambda = (\lambda_1, ..., \lambda_k)\).
We write \(\mathcal{P} := \mathcal{P}_{J(\lambda)}\), and \(A_{a,b} := A_{J(\lambda), a, b}\).
And as before, \((e_{ij})_{ij}\) and \((f_j)_j\) form the standard basis for \(\mathbb{C}^{m + n}\).
\subsection{The components of \(\mathcal{Q}_{wr}\)}
Recall from section 5 the varieties
\[\mathcal{Q}_{wr} = \{(A_{e_{wr}, b}, (V_i)) \in \mathcal{P}\}.\]
Fix any \(w,r\).
\cref{a_zero} tells us that 
\[\mathcal{Q}_{wr} \cong \mathcal{Q}' := \{(A'_{X', 0, b}, (V_i)) : \forall i. \; A'_{X', 0, b} V_{i + 1} \subseteq V_i\},\]
where \(X' = J(\lambda')\), and \(\lambda' = (\lambda_1, ..., \lambda_w - r, ..., \lambda_k)\), and \(m' = m - r\), and \(n' = n + r\).
\par Let \((\mathcal{Q}'_{I, (\rho_i), \alpha})_{I, (\rho_i), \alpha}\) be the irreducible components of \(\mathcal{Q}'\) give by \cref{Q_comps}.
Write \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\) to denote the irreducible component of \(\mathcal{Q}_{wr}\) corresponding to \(\mathcal{Q}'_{I, (\rho_i), \alpha}\) via the isomorphism \(\mathcal{Q}_{wr} \cong \mathcal{Q}'\) of \cref{a_zero}.

\begin{corollary}
    The irreducible components of \(\mathcal{Q}_{wr}\) are exactly the subvarieties \(\mathcal{Q}_{w,r,I,(\rho_i),\alpha}\).
    Each has dimension \(\sum_{ij} \min(\lambda_i', \lambda_j')\), where \(\lambda' = (\lambda_1, ..., \lambda_{w - 1}, \lambda_w - r, \lambda_{w + 1}, ..., \lambda_k)\).
\end{corollary}
\begin{proof}
    From the foregoing discussion, it is clear that they are indeed the irreducible components.
    To calculate the dimension, we refer to \cref{u_i_rho_irred_and_dim}, which says the dimension is \(\gamma([0, \lambda_1', ..., \lambda_k'])\).
\end{proof}

\par In section 5 we defined the subvarieties \(\mathcal{P}_{wr} \subseteq \mathcal{P}\) and the principal \(G_{wr}\)-bundle \(\varphi_{wr} : \mathcal{Q}_{wr} \times G \to \mathcal{P}_{wr}\).
